\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-09-16 doc/USER_MANUAL/02_getting_started.tex
adds AMD MI250 configuration support (for Frontier)

The same applies to compilation for AMD cards with HIP:
\begin{verbatim}
  ./configure --with-hip ..
\end{verbatim}
or
\begin{verbatim}
  ./configure --with-hip=MI8 ..
\end{verbatim}
where for example \texttt{MI8,MI25,MI50,MI100,..} specifies the target GPU architecture of your card.\\

>>>>

The same applies to compilation for AMD cards with HIP:
\begin{verbatim}
  ./configure --with-hip ..
\end{verbatim}
or
\begin{verbatim}
  ./configure --with-hip=MI8 ..
\end{verbatim}
where for example \texttt{MI8,MI25,MI50,MI100,MI250,..} specifies the target GPU architecture of your card.
Additional compilation flags can be added by specifying \texttt{HIP\_FLAGS}, as for example:
{\small
\begin{verbatim}
  ./configure --with-hip=MI250 \
      HIP_FLAGS="-fPIC -ftemplate-depth-2048 -fno-gpu-rdc -std=c++17 \
                 -O2 -fdenormal-fp-math=ieee -fcuda-flush-denormals-to-zero -munsafe-fp-atomics" \
      ..
\end{verbatim}
}
